### 2015-07-03 doc/notebook/2015-02-26_Bacterial_data_acquisition.Rmd
Add groupings defined by Rene

@@

#... and we output a group file to use for splitting up the list file
write.table(file="data/mothur/bacteria.category.groups", x=cbind(rownames(metadata), metadata$category), quote=FALSE, row.names=FALSE, col.names=FALSE, sep="\t")
```

One thing we'd like to look at are the rarefaction curves for each environmental category. To do this we'll run the mothur command like so..

```{r, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur);
        make.shared(list=all_bacteria.filter.unique.precluster.an.list, group=bacteria.category.groups, label=unique-0.03-0.05-0.10-0.20);
        rarefaction.single(shared=all_bacteria.filter.unique.precluster.an.shared)"
```

>>>>

#correct typos:
metadata$category[metadata$category == 'AF'] <- 'AE'
metadata$category[metadata$category == 'AQBF'] <- 'AQB'
metadata$category[metadata$category == 'AQD'] <- 'AQO'
metadata$category[metadata$category == 'AQHS'] <- 'AQH'
metadata$category[metadata$category == 'AQS'] <- 'AQMS'
metadata$category[metadata$category == 'AWF'] <- 'AQF'
metadata$category[metadata$category == 'DS'] <- 'BS'
metadata$category[metadata$category == 'S'] <- 'SO'
metadata$category[metadata$category == 'SI'] <- 'BI'
metadata$category[metadata$category == 'V'] <- 'BO'
metadata$category[metadata$category == 'VD'] <- 'BD'
metadata$category[metadata$category == 'ZOZO'] <- 'ZO'
metadata$category[metadata$category == 'AH'] <- 'AQH'
metadata$category[metadata$category == 'AQOS'] <- 'AQS'
metadata$category[metadata$category == 'BS'] <- 'BD'

@@

#... and we output a group file to use for splitting up the list file into the individual categories...
write.table(file="data/mothur/bacteria.all_category.groups", x=cbind(rownames(metadata), metadata$category), quote=FALSE, row.names=FALSE, col.names=FALSE, sep="\t")

#... and we output a group file to use for splitting up the list file into the pooled categories...
#   For bacteria: AQF, AQFS, AQM, AQMS, BD, BI, BP, OT, PR, SO, ZO, and ZV and the others into one category
#   per Rene 6/24/2015...
pool1 <- c("AQF", "AQFS", "AQM", "AQMS", "BD", "BI", "BP", "OT", "PR", "SO", "ZO", "ZV")
pool_categories <- rep(NA, nrow(metadata))
pool_categories[metadata$category %in% pool1] <- "pool1"
pool_categories[!metadata$category %in% pool1] <- "pool2"
pool_categories[is.na(metadata$category)] <- "NA"
write.table(file="data/mothur/bacteria.pool_category.groups", x=cbind(rownames(metadata), pool_categories), quote=FALSE, row.names=FALSE, col.names=FALSE, sep="\t")

#... and we pool the categories by environment
env_categories <- rep(NA, nrow(metadata))
env_categories[metadata$category == "AE"] <- "aerosol"
env_categories[metadata$category == "OT"] <- "other"
env_categories[metadata$category %in% c("AQB", "AQBS", "AQF", "AQFS", "AQH", "AQI", "AQM", "AQMS", "AQO", "AQS")] <- "aquatic"
env_categories[metadata$category %in% c("BD", "BF", "BI", "BO", "BP")] <- "built"
env_categories[metadata$category %in% c("PO", "PR", "PS")] <- "plant"
env_categories[metadata$category %in% c("SA", "SD", "SO", "SP")] <- "soil"
env_categories[metadata$category %in% c("ZA", "ZN", "ZO", "ZV")] <- "zoonotic"
write.table(file="data/mothur/bacteria.env_category.groups", x=cbind(rownames(metadata), env_categories), quote=FALSE, row.names=FALSE, col.names=FALSE, sep="\t")
```

One thing we'd like to look at are the rarefaction curves for each set of group files and the entire dataset. To do this we'll run the mothur command like so..

```{r, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur);
        make.shared(list=all_bacteria.filter.unique.precluster.an.list, group=bacteria.all_category.groups, label=unique-0.03-0.05-0.10-0.20);
        system(mv data/mothur/all_bacteria.filter.unique.precluster.an.shared data/mothur/all_bacteria.all_categories.shared);
        rarefaction.single(shared=all_bacteria.all_categories.shared);
        summary.single(shared=all_bacteria.all_categories.shared, calc=nseqs-sobs-coverage)"

mothur "#set.dir(input=data/mothur, output=data/mothur);
        make.shared(list=all_bacteria.filter.unique.precluster.an.list, group=bacteria.pool_category.groups, label=unique-0.03-0.05-0.10-0.20);
        system(mv data/mothur/all_bacteria.filter.unique.precluster.an.shared data/mothur/all_bacteria.pool_category.shared);
        rarefaction.single(shared=all_bacteria.pool_category.shared);
        summary.single(shared=all_bacteria.pool_category.shared, calc=nseqs-sobs-coverage)"

mothur "#set.dir(input=data/mothur, output=data/mothur);
        make.shared(list=all_bacteria.filter.unique.precluster.an.list, group=bacteria.env_category.groups, label=unique-0.03-0.05-0.10-0.20);
        system(mv data/mothur/all_bacteria.filter.unique.precluster.an.shared data/mothur/all_bacteria.env_category.shared);
        rarefaction.single(shared=all_bacteria.env_category.shared);
        summary.single(shared=all_bacteria.env_category.shared, calc=nseqs-sobs-coverage)"

mothur "#rarefaction.single(list=data/mothur/all_bacteria.filter.unique.precluster.an.list, label=unique-0.03-0.05-0.10-0.20);"
```

### 2015-07-03 doc/notebook/2015-03-13_Archaeal_data_acquisition.Rmd
Add groupings defined by Rene

@@

#... and we output a group file to use for splitting up the list file
write.table(file="data/mothur/archaea.category.groups", x=cbind(rownames(metadata), metadata$category), quote=FALSE, row.names=FALSE, col.names=FALSE, sep="\t")
```

One thing we'd like to look at are the rarefaction curves for each environmental category. To do this we'll run the mothur command like so..

```{r, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur);
        make.shared(list=all_archaea.filter.unique.precluster.an.list, group=archaea.category.groups, label=unique-0.03-0.05-0.10-0.20);
        rarefaction.single(shared=all_archaea.filter.unique.precluster.an.shared)"
```

>>>>

#correct typos:
metadata$category[metadata$category == 'AQD'] <- 'AQO'
metadata$category[metadata$category == 'AQHS'] <- 'AQH'
metadata$category[metadata$category == 'AQS'] <- 'AQMS'
metadata$category[metadata$category == 'VD'] <- 'BD'
metadata$category[metadata$category == 'BM'] <- 'BI'
metadata$category[metadata$category == 'AH'] <- 'AQH'

@@

#... and we output a group file to use for splitting up the list file into the individual categories...
write.table(file="data/mothur/archaea.all_category.groups", x=cbind(rownames(metadata), metadata$category), quote=FALSE, row.names=FALSE, col.names=FALSE, sep="\t")

#... and we output a group file to use for splitting up the list file into the pooled categories...
#   For archaea: AQH, AQM, AQMS, and ZV into one. the rest into the other
#   per Rene 6/24/2015...
pool1 <- c("AQH", "AQM", "AQMS", "ZV")
pool_categories <- rep(NA, nrow(metadata))
pool_categories[metadata$category %in% pool1] <- "pool1"
pool_categories[!metadata$category %in% pool1] <- "pool2"
pool_categories[is.na(metadata$category)] <- "NA"
write.table(file="data/mothur/archaea.pool_category.groups", x=cbind(rownames(metadata), pool_categories), quote=FALSE, row.names=FALSE, col.names=FALSE, sep="\t")

#... and we pool the categories by environment
env_categories <- rep(NA, nrow(metadata))
env_categories[metadata$category == "AE"] <- "aerosol"
env_categories[metadata$category == "OT"] <- "other"
env_categories[metadata$category %in% c("AQB", "AQBS", "AQF", "AQFS", "AQH", "AQI", "AQM", "AQMS", "AQO", "AQS")] <- "aquatic"
env_categories[metadata$category %in% c("BD", "BF", "BI", "BO", "BP")] <- "built"
env_categories[metadata$category %in% c("PO", "PR", "PS")] <- "plant"
env_categories[metadata$category %in% c("SA", "SD", "SO", "SP")] <- "soil"
env_categories[metadata$category %in% c("ZA", "ZN", "ZO", "ZV")] <- "zoonotic"
write.table(file="data/mothur/archaea.env_category.groups", x=cbind(rownames(metadata), env_categories), quote=FALSE, row.names=FALSE, col.names=FALSE, sep="\t")
```

One thing we'd like to look at are the rarefaction curves for each set of group files and the entire dataset. To do this we'll run the mothur command like so..

```{r, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur);
        make.shared(list=all_archaea.filter.unique.precluster.an.list, group=archaea.all_category.groups, label=unique-0.03-0.05-0.10-0.20);
        system(mv data/mothur/all_archaea.filter.unique.precluster.an.shared data/mothur/all_archaea.all_categories.shared);
        rarefaction.single(shared=all_archaea.all_categories.shared);
        summary.single(shared=all_archaea.all_categories.shared, calc=nseqs-sobs-coverage)"

mothur "#set.dir(input=data/mothur, output=data/mothur);
        make.shared(list=all_archaea.filter.unique.precluster.an.list, group=archaea.pool_category.groups, label=unique-0.03-0.05-0.10-0.20);
        system(mv data/mothur/all_archaea.filter.unique.precluster.an.shared data/mothur/all_archaea.pool_category.shared);
        rarefaction.single(shared=all_archaea.pool_category.shared);
        summary.single(shared=all_archaea.pool_category.shared, calc=nseqs-sobs-coverage)"

mothur "#set.dir(input=data/mothur, output=data/mothur);
        make.shared(list=all_archaea.filter.unique.precluster.an.list, group=archaea.env_category.groups, label=unique-0.03-0.05-0.10-0.20);
        system(mv data/mothur/all_archaea.filter.unique.precluster.an.shared data/mothur/all_archaea.env_category.shared);
        rarefaction.single(shared=all_archaea.env_category.shared);
        summary.single(shared=all_archaea.env_category.shared, calc=nseqs-sobs-coverage)"

mothur "#rarefaction.single(list=data/mothur/all_archaea.filter.unique.precluster.an.list, label=unique-0.03-0.05-0.10-0.20);"
```
